---
title: "Markets - Data"
author: "Dhruv Haldar (haldar@kth.se)"
date: "`r Sys.Date()`"
output:
  html_document:
    css: style.css
  pdf_document:
    latex_engine: xelatex
geometry: margin=0.5cm
runtime: shiny
---

## <span style='color: #bf6900'> Option Data

### Option Chain

```{r error=FALSE, message=FALSE, warning=FALSE, , echo=FALSE, include=FALSE}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org "
options(repos = r)
library(reticulate)
```

```{python optionschain_p, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, ,echo=FALSE, tidy=TRUE}
# Python program to print
# colored text and background
def strBold(skk):        return "\033[1m {}\033[0m".format(skk)

# Libraries
import requests
import json
import math

# Method to get nearest strikes
def round_nearest(x,num=50): return int(math.ceil(float(x)/num)*num)
def nearest_strike_bnf(x): return round_nearest(x,100)
def nearest_strike_nf(x): return round_nearest(x,50)

# Urls for fetching Data
url_oc      = "https://www.nseindia.com/option-chain"
url_bnf     = 'https://www.nseindia.com/api/option-chain-indices?symbol=BANKNIFTY'
url_nf      = 'https://www.nseindia.com/api/option-chain-indices?symbol=NIFTY'
url_indices = "https://www.nseindia.com/api/allIndices"

# Headers
headers = {'user-agent': 'Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/80.0.3987.149 Safari/537.36',
            'accept-language': 'en,gu;q=0.9,hi;q=0.8',
            'accept-encoding': 'gzip, deflate, br'}

sess = requests.Session()
cookies = dict()

# Local methods
def set_cookie():
    request = sess.get(url_oc, headers=headers, timeout=5)
    cookies = dict(request.cookies)

def get_data(url):
    set_cookie()
    response = sess.get(url, headers=headers, timeout=5, cookies=cookies)
    if(response.status_code==401):
        set_cookie()
        response = sess.get(url_nf, headers=headers, timeout=5, cookies=cookies)
    if(response.status_code==200):
        return response.text
    return ""

def set_header():
    global bnf_ul
    global nf_ul
    global bnf_nearest
    global nf_nearest
    response_text = get_data(url_indices)
    data = json.loads(response_text)
    for index in data["data"]:
        if index["index"]=="NIFTY 50":
            nf_ul = index["last"]
        if index["index"]=="NIFTY BANK":
            bnf_ul = index["last"]
    bnf_nearest=nearest_strike_bnf(bnf_ul)
    nf_nearest=nearest_strike_nf(nf_ul)

# Showing Header in structured format with Last Price and Nearest Strike

def print_header(index="",ul=0,nearest=0):
    print(str( index.ljust(12," ") + " => ")+ str(" Last Price: ") + str(ul) + str(" Nearest Strike: ") + str(nearest))

def print_hr():
    print(str("|".rjust(70,"-")))

# Fetching CE and PE data based on Nearest Expiry Date
def print_oi(num,step,nearest,url):
    strike = nearest - (step*num)
    start_strike = nearest - (step*num)
    response_text = get_data(url)
    data = json.loads(response_text)
    currExpiryDate = data["records"]["expiryDates"][0]
    for item in data['records']['data']:
        if item["expiryDate"] == currExpiryDate:
            if item["strikePrice"] == strike and item["strikePrice"] < start_strike+(step*num*2):
                #print(str(str(item["strikePrice"])) + str(" CE ") + "[ " + strBold(str(item["CE"]["openInterest"]).rjust(10," ")) + " ]" + strRed(" PE ")+"[ " + strBold(str(item["PE"]["openInterest"]).rjust(10," ")) + " ]")
                print(data["records"]["expiryDates"][0] + " " + str(item["strikePrice"]) + " CE " + "[ " + str(item["CE"]["openInterest"]).rjust(10," ") + " ]" + " PE " + "[ " + strBold(str(item["PE"]["openInterest"]).rjust(10," ")) + " ]")
                strike = strike + step

# Finding highest Open Interest of People in CE based on CE data         
def highest_oi_CE(num,step,nearest,url):
    strike = nearest - (step*num)
    start_strike = nearest - (step*num)
    response_text = get_data(url)
    data = json.loads(response_text)
    currExpiryDate = data["records"]["expiryDates"][0]
    max_oi = 0
    max_oi_strike = 0
    for item in data['records']['data']:
        if item["expiryDate"] == currExpiryDate:
            if item["strikePrice"] == strike and item["strikePrice"] < start_strike+(step*num*2):
                if item["CE"]["openInterest"] > max_oi:
                    max_oi = item["CE"]["openInterest"]
                    max_oi_strike = item["strikePrice"]
                strike = strike + step
    return max_oi_strike

# Finding highest Open Interest of People in PE based on PE data 
def highest_oi_PE(num,step,nearest,url):
    strike = nearest - (step*num)
    start_strike = nearest - (step*num)
    response_text = get_data(url)
    data = json.loads(response_text)
    currExpiryDate = data["records"]["expiryDates"][0]
    max_oi = 0
    max_oi_strike = 0
    for item in data['records']['data']:
        if item["expiryDate"] == currExpiryDate:
            if item["strikePrice"] == strike and item["strikePrice"] < start_strike+(step*num*2):
                if item["PE"]["openInterest"] > max_oi:
                    max_oi = item["PE"]["openInterest"]
                    max_oi_strike = item["strikePrice"]
                strike = strike + step
    return max_oi_strike

set_header()
#print('\033c')
#print_hr()
print("Nifty")
#print_hr()
print_oi(10,50,nf_nearest,url_nf)
#print_hr()
print("Bank Nifty")
#print_hr()
print_oi(10,100,bnf_nearest,url_bnf)
#print_hr()

# Finding Highest OI in Call Option In Nifty
nf_highestoi_CE = highest_oi_CE(10,50,nf_nearest,url_nf)

# Finding Highest OI in Put Option In Nifty
nf_highestoi_PE = highest_oi_PE(10,50,nf_nearest,url_nf)

# Finding Highest OI in Call Option In Bank Nifty
bnf_highestoi_CE = highest_oi_CE(10,100,bnf_nearest,url_bnf)

# Finding Highest OI in Put Option In Bank Nifty
bnf_highestoi_PE = highest_oi_PE(10,100,bnf_nearest,url_bnf)

```

## Option Chain Technical Analysis {#option-technical-analysis}

| Option Property            | Value                   |
|----------------------------|-------------------------|
| Nifty Last Price           | `r factor(py$nf_ul)`    |
| Nifty Nearest Strike       | `r py$nf_nearest`       |
| Nifty Major Support        | `r py$nf_highestoi_PE`  |
| Nifty Major Resistance     | `r py$nf_highestoi_CE`  |
| BankNifty Last Price       | `r factor(py$bnf_ul)`   |
| BankNifty Nearest Strike   | `r py$bnf_nearest`      |
| BankNifty Major Support    | `r py$bnf_highestoi_PE` |
| Banknifty Major Resistance | `r py$bnf_highestoi_CE` |

```{r error=FALSE, message=FALSE, warning=FALSE, include=FALSE}
packages <- function()
{
  # Package names
packages <- c("ggplot2", 
              #"bslib",
              "shiny",
              "readxl", 
              "nser", 
              "lattice", 
                "reshape2", 
                #"hablar", 
                "dplyr", 
                #"tidyquant",
                "tidyverse", 
                "scales",
                "padr",
              "curl",
                #"purrr",
                #"svDialogs",
                "utils", 
                "quantmod",
              "broom", 
              #"magrittr",
                "diffr", 
                "plotly",
                #"diffobj",
                "alphavantager",
                "plotly",
                "ggpubr",
                #"derivmkts",
                #"TTR",
                "optionstrat",
                #"knitr",
                #"rmarkdown",
              "PerformanceAnalytics",
              "dygraphs",
              "reticulate",
                "nse2r",
              "tidyverse"
                )
  
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
    install.packages(packages[!installed_packages])
  }
  
# Packages loading
invisible(lapply(packages, library, character.only = TRUE))
  
# Alpha Vantage API key
api_key="MB7IR06HYB54IUJG"
av_api_key(api_key)
  }
netFIIDIIfn <- function(fdii) #function
{
date = fdii[3:20,1]
date <- gsub("-", "", date)                        # Applying gsub function
date = as.Date(date, "%d%b%y")
net_FII = fdii[3:20,4]
net_FII = factor(net_FII)
net_FII <- gsub(",","", net_FII)                   # Applying gsub function
options(digits=7)
net_FII=as.double(net_FII)
net_DII = fdii[3:20,7]
net_DII = factor(net_DII)
net_DII <- gsub(",","", net_DII)                   # Applying gsub function
options(digits=7)
net_DII=as.double(net_DII)
fdii_main <- data.frame(date,net_FII,net_DII)
#netFII+netDII
fig.align = 'right'
p <- ggplot(fdii_main,aes(x = date, y = net_FII+net_DII)) 
#geom_text(aes(label=net_FII+net_DII),nudge_x = 0,
#            nudge_y = 0,angle=45,vjust=0.5) 
#  
p + geom_bar(aes(fill = net_FII), stat = "identity") + theme_dark() + labs(x = "Date", y = "Gross Purchase (Crores)",subtitle = paste("Last updated",Sys.time())) + geom_text(aes(label=net_FII+net_DII),colour='#D2CCA1') + guides(x = guide_axis(n.dodge = 2)) + scale_x_date(date_labels="%b %d",date_breaks  ="1 day")  
}
```

### Option Profitability Calculator (later)

### Option Strategy (later)

#### Strangle (later)

#### Bear Call Spread (later)

#### Bull Call Spread (later)

#### Bear Put Spread (later)

#### Bull Put Spread (later)

```{r}
optionprice=50
optionprice <- as.tibble(optionprice)
```

| Calculator (later) | Value (later)               |
|--------------------|-----------------------------|
| 50% Profit         | `r print(0.05*optionprice)` |
| 30% Loss           | `r print(0.03*optionprice)` |
| Profitability      | `r print(paste("45","%"))`  |

Black Scholes (later)

```{r blackscholes, eval=FALSE, error=FALSE, message=FALSE, warning=FALSE, include=FALSE}
BlackScholes <- function(S, K, r, T, sig, type){
  
  if(type=="C"){
  d1 <- (log(S/K) + (r + sig^2/2)*T) / (sig*sqrt(T))
  d2 <- d1 - sig*sqrt(T)
  
  value <- S*pnorm(d1) - K*exp(-r*T)*pnorm(d2)
  return(value)}
  
  if(type=="P"){
  d1 <- (log(S/K) + (r + sig^2/2)*T) / (sig*sqrt(T))
  d2 <- d1 - sig*sqrt(T)
  
  value <-  (K*exp(-r*T)*pnorm(-d2) - S*pnorm(-d1))
  return(value)}
}

call <- BlackScholes(110,100,0.04,1,0.2,"C")
put <- BlackScholes(110,100,0.04,1,0.2,"P")

print(call)
print(put)
```

### <span style='color: #bf6900'> FII & DII Trading Activity

```{r echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
fdii <- function()
{
  if(!require('rvest')) 
    {
    install.packages('rvest')
    library('rvest')
    }
   url = 'https://www.moneycontrol.com/stocks/marketstats/fii_dii_activity/index.php'
  dat = url %>%
  read_html() %>%
  html_nodes(xpath='//*[@id="fidicash"]/div') %>%
  html_table()

  dat = dat[[1]]
  dat = as.data.frame(dat)
  dat = dat[-c(3,4,5),]
  nam = c("DATE", "FII Rs Crores" ,"FII Rs Crores" ,"FII Rs Crores" ,"DII Rs Crores", "DII Rs Crores" ,"DII Rs Crores")
  dat = `colnames<-`(dat, nam)
  DATE = str_extract(dat$DATE, '[^_\n]+')
  dat = dat[,-1]
  dat = cbind(DATE, dat)
  dat[1,1] = ""
  row.names(dat) <- NULL
  return(dat)
}

data_bhavtoday_nser <- function() #function
{
  get_data <- function(get_data) 
    {
#FO Bhavcopy Today (updated every evening,not working in weekend)
    fobhavtoday <-- fobhavtoday()

#Indices Data
    fo_indices = fobhavtoday[1:19,]
    }
  get_data2 <- possibly(get_data, otherwise = NA)
  fobhavtoday
  }

# FO Bhavcopy Hist. (1 Jan 2016 Onwards)
Hist_date=28042022
data_bhavtoday_nser <- function() #function
{
  fobhavhist = fobhav(Hist_date)
  bhavhist = bhav(Hist_date)
  fobhavhist
}

# Heatmap
markets_heatmap <- function() #function
{
  nsetree = nsetree()
}
fo_heatmap <- function() #function
{
  nsetreefo = nsetree("fo")
}

# NSE Indices today
cashmarkets_stocks <- function() #function
{
  nseindex = nseindex()
  nseindex_name = nseindex[1:55,1]
  nseindex_change = nseindex[1:55,4]
  nseindex = nse_index_quote(clean_names = TRUE)

#Stock symbol list
  nsestockcode = nse_stock_code(clean_names = TRUE)

#Stock price
  stock_code="SCHAEFFLER"
  stock_price = nse_stock_quote(stock_code, source = c("yahoo",
                                                       "rediff"))
  print(paste(stock_code,"is trading at",
            stock_price,"INR at NSE",", last updated",Sys.time()))

#52 Week high
  nseyearhigh = nse_stock_year_high(clean_names = TRUE)
#52 Week low
  nseyearlow = nse_stock_year_low(clean_names = TRUE)
#Most Traded Stocks
  nsemosttraded = nse_stock_most_traded(clean_names = TRUE)
#Top Gainers
  nsetopgainers = nse_stock_top_gainers(clean_names = TRUE)
#Top Losers
  nsetoplosers = nse_stock_top_losers(clean_names = TRUE)
}
#Function Calls
packages()
fdii = fdii()
netFIIDIIfn(fdii)

```

## <span style='color: #bf6900'>Preopen NSE FO Markets

### <span style='color: #73C1C6'> NSE FO Top Gainers

```{r nse_fo_top_gainers, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE,escape = FALSE}
options(warn=-1) #supress coercion warnings, fix later
  #nseopen_fo = nseopen("fo") #FO stocks
library(kableExtra)
library(nse2r)
#nse_fo_top_gainers$percent_change=  cell_spec(nse_fo_top_gainers$percent_change, color = ifelse(nse_fo_top_gainers$percent_change > 0.1, "red", "blue"))

knitr::kable(nse_fo_top_gainers(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "600px")
```

### <span style='color: #e83151'> NSE FO Top Losers

```{r nse_fo_top_losers, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::kable(nse_fo_top_losers(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "600px")
```

## <span style='color: #bf6900'> NSE Indices

### Preopen Nifty

```{r nse_preopen_nifty, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
knitr::kable(nse_preopen_nifty(clean_names = TRUE))%>% #preopen NIFTY
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "600px")
```

### Preopen Nifty Bank

```{r nse_preopen_niftybk, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_preopen_nifty_bank(clean_names = TRUE))%>% #preopen
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "50%")
```

### NSE Index

```{r nse_index, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_index_quote(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "50%", height = "200px")
```

## <span style='color: #bf6900'> Most Traded Stocks {#span-stylecolor-bf6900-most-traded-stocks}

```{r nse_most_traded, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_stock_most_traded(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "80%", height = "50%")
```

## <span style='color: #bf6900'>NSE IPO

```{r nse_ipo, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
#knitr::kable(nselive()) #Nifty stocks
library(kableExtra)
library(nser)
knitr::kable(nseipo())%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)
```

## <span style='color: #bf6900'>NSE Cash Market

### Advances Declines

```{r advdec, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_advances_declines(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "50%", height = "600px")
```

### 52 Week high

```{r 52wkhigh, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_stock_year_high(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "600px")
```

### 52 Week low

```{r 52wklow, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_stock_year_low(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "600px")
```

### Top Gainers

```{r topgainers, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_stock_top_gainers(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "400px")
```

### Top Losers

```{r toplosers, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
knitr::kable(nse_stock_top_losers(clean_names = TRUE))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "100%", height = "400px")
```

## NIFTY PE from `2022-1-1` to `2022-5-9`

```{python include=FALSE, tidy=TRUE}
#Python Nifty PE Script
#pip install nsepy
from datetime import date
# Index P/E ratio history
from nsepy import get_index_pe_history
nifty_pe = get_index_pe_history(symbol="NIFTY",
                                start=date(2022,1,1),
                                end=date(2022,5,9))
print(nifty_pe)
```

```{r nifty_pe_r, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='asis', tidy=TRUE}
pythonr <- py$nifty_pe
knitr::kable(pythonr)%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = F
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "170px", height = "350px")
```

## <span style='color: #bf6900'>RBI Current Data

```{python rbidata_python, include=TRUE, echo=FALSE, tidy=TRUE}
#no module named jugaad_data
#pip install jugaad-data
#Goto System tools set Python 2nd option (system interpreter) as default
from jugaad_data.rbi import RBI
r = RBI()
rbi = r.current_rates()
```

```{r rbidata_r, echo=FALSE, error=FALSE, warning=FALSE, paged.print=FALSE, results='hold', tidy=TRUE}
python_rbi_value <- py$rbi
python_rbi_value[8:11] <- NULL
python_rbi_value[22:23] <- NULL
python_rbi_value <- unlist(python_rbi_value)

knitr::kable(python_rbi_value,
             col.names = c("Values"))%>%
  kable_styling(bootstrap_options = "condensed",
                , full_width = T
                ,font_size = 12,
                fixed_thead = T)%>%
scroll_box(width = "310px", height = "600px")
```

```{r include=FALSE, echo=FALSE, error=FALSE, warning=FALSE}
library(tibble)
ticker <- "HDFCBANK.NS"
getSymbols(ticker,src='yahoo')
ticker <- as.tibble(ticker)
```

## `r ticker$value` Stock Ticker

```{r echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
# trace example of ohlc charts
df <- data.frame(Date=index(ticker),coredata(ticker))
df <- tail(df, 182)

fig <- df %>% plot_ly(x = ~Date, type="candlestick",
                       open = ~ticker.Open, close = ~ticker.Close,
                       high = ~ticker.High, low = ~ticker.Low) 
fig <- fig %>% add_lines(x = ~Date, y = ~ticker.Open, line = list(color = 'black', width = 0.75), inherit = F)
fig <- fig %>% layout(showlegend = FALSE)

fig

```

## NSE Fundamentals do later

```{r nsefundamentals, eval=FALSE, error=FALSE, message=FALSE, warning=FALSE, include=FALSE}
get.nse.ratios <- function(index.nse = 'NIFTY 50', date.start = as.Date('2001-01-01'), date.end = as.Date(Sys.time())){
  # url.base <- 'https://www1.nseindia.com/products/content/equities/indices/historical_pepb.htm'
  index.nse <- gsub(' ', '%20', index.nse)
  
  # Split Date range into acceptable range
  max.history.constraint <- 100
  dates.start <- seq.Date(date.start, date.end, by = max.history.constraint)
  data.master <- data.frame()
  # Loop over sub-periods to extract data
  for(fromDate in dates.start){
    toDate <- min(fromDate+(max.history.constraint - 1), as.Date(Sys.Date()))
    
    cat(sprintf('Fetching data from %s to %s \n', as.Date(fromDate), as.Date(toDate)))
    # browser()
    # Reformat dates
    fromDate <- format.Date(as.Date(fromDate), '%d-%m-%Y')
    toDate <- format.Date(as.Date(toDate), '%d-%m-%Y')
    
    # Infer url for sub-period
    url.sub <- sprintf("https://www1.nseindia.com/products/dynaContent/equities/indices/historical_pepb.jsp?indexName=%s&fromDate=%s&toDate=%s&yield1=undefined&yield2=undefined&yield3=undefined&yield4=all", index.nse, fromDate, toDate)
    
    # Scrape table from inferred url
    data.sub <- rvest::html_table(xml2::read_html(url.sub))[[1]]
    
    # Clean the table
    names.columns <- unname(unlist(data.sub[2,]))
    data.clean <- data.sub[3:(nrow(data.sub)-1),]
    colnames(data.clean) <- names.columns
    data.clean$Date <- as.Date(data.clean$Date, format = '%d-%b-%Y')
    cols.num <- names(which(sapply(data.clean, class) == 'character'))
    data.clean[cols.num] <- sapply(data.clean[cols.num],as.numeric)
    
    # Append to master data
    data.master <- rbind(data.master, data.clean)

  }
  
  data.master
}
```
